Robust Adaptation to Multi-Scale Climate Variability

### 2019-03-27 report-earths-future/reviewer-response.md

# Response to Reviewers

We thank

## Reviewer 1

### Overall comments

I enjoyed reading this paper, which confirms that uncertainty dominates when predicting climate change over an extended lead time.

The analysis is carried out through a series of synthetic experiments.
It is interesting to see what are the limits of predictability in the presence of natural variability and secular change.

I think this paper is timely in that it confirms that particular care should be taken when making long term predictions in the presence of a changing climate.
As the analysis clearly shows, it is not easy to recognize climate signals.
Natural variability may interact with climate change therefore masking inherent behaviours.

I think the paper is well written and organized. I made some comments in the attached pdf file.
My comments are essentially minor.

I would like to point out that I missed in the paper a discussion on the Hurst effect.
There is an extended literature on it. Such effect implies the presence of low frequency variability (long term cycles) which were observed in several secular time series of environmental variables.
The Hurst effect may be difficult to distinguish from anthropogenic climate change (ACC).
This effect is ignored by several climate studies. I believe this paper would be a good opportunity to discuss the interaction of the Hurst effect with ACC.
To this end, a proper discussion should be included in the manuscript.

I would like to congratulate the authors for their interesting work.

Best regards,
Alberto Montanari

### Line comments

7: It is not clear to me what this key point means

> We have updated this key point following suggestions from reviewer 2

10: I believe these key points are not much informative. I am not sure of my opinion, but my feeling it that they should reformulated to better explain what the paper discovered.

> Working on it!

34: What do you mean exactly? I don't think mitigation efforts proved to be successful.

> We (unfortunately!) agree that mitigation efforts have not yet proven successful. We have re-phrased this sentence. It now reads "Even if future mitigation efforts are successful, existing levels of atmospheric CO2 and ocean heat content mean that novel adaptation strategies are needed."

84: I believe the impact of ACC on floods and drought is far from being well documented. It is not yet clear whether droughts like the Millenium Drought and the Californian drought have been caused by ACC. California is subjected to drought since the XIX century. Please see  https://en.wikipedia.org/wiki/Droughts_in_California and references therein.

> We agree with the reviewer that the influence of ACC on hydrological extremes is unclear and complex. We have re-worded this sentence to be more clear about this point.  It now reads "Of these processes, ACC has received the most attention in the climate adaptation literature and its influence on some river floods, droughts, hurricanes, urban flooding, and many other climate hazards has been the subject of substantial investigation..."

87: I fully agree with this sentence.

> Thank you very much

103: LFV is strictly related to the Hurst effect. There is an extended literature. I think a mention to the Hurst effect would be appropriate here.

> We have added a short paragraph here which seeks to join some disparate literatures on paleoclimate, Hurst effects, and ocean-atmosphere dynamics. These all explain similar phenomena but use different perspectives.

115: I am not sure it is appropriate to make mention to a hypothetically perfect climate model. It should be made clear that this is a VERY ideal assumption. Perfect environmental models do not exist and, as hydrologists, we should be clear on that.

> We strongly agree with this assessment. In a presentation of this paper at the 2018 AGU Fall Meeting we referred to opening a bottle on a beach and using one of three wishes granted by a magical genie on a climate model to emphasize the ridiculousness of having a perfect model. In this slightly more formal setting we have re-worded the sentence to "Even in the idealized, and unrealistic, case of a perfect climate model, these uncertainties will be large."

118: This is why I believe we should not make reference to perfect models.

> See previous comment

231: I believe these details on the software should not be given here, in the body of the paper. These may be part of the user guide of the produced software

> We are deferring here to the editor. However, I feel that as a consumer of open source software I have an ethical responsibility to cite the primary packages that I use. Further, as a scientist committed to reproducibility I believe that describing software used is as important as describing the experiment design. However, making code accessible on GitHub partially alleviates this concern.

## Reviewer 2

### Overall comments

The authors have teased apart climatic risks that are considered for planning purposes across multiple time horizons.
It is an interesting exploration the interaction of various types of climatic variability, planning horizons, and length of time series, and how this interaction impacts the choice of instruments of climate risk mitigation.
As this paper uses the word robust in the title, the introduction needs to link the concept of robustness to their questions and methods.
Suggest citing literature on robust adaptation if you keep ‘robust’ in the title.

> We have updated the key point in the summary

In Sections 2.1 and 2.2 you describe the three models of climatic change, and three ways of modeling each climate model.
Is there a way to clarify the structure of your computational experiment in these two sections, including your intent of using multiple methods of generating these types of climate variability?
Please explicitly link the lognormal model with the LN2 acronym in text before using in figures.

It would be interesting to see whether there is a relationship in the results between bias and variance; e.g. can the variance inform or predict the bias in each of the three types of climate variability?

The discussion needs to reference the computational results, at minimum to justify the computational experiment as opposed to solely a conceptual exploration.

### Key points

To me, planning implies a process rather than the expected lifespan of a project.
Can you clarify which meaning you use?
If the latter, perhaps the following would be more readable: Climate risk varies over the planned lifespan of a project.
This can also be clarified in other locations of the paper, e.g. line 364 in the summary.

### Line comments

15-16: Can you restate phrase copied below, unclear terms in bold:
**the role of low-frequency variability in modulating climate extremes**

> We agree and have re-phrased this sentence. It now reads "... historical and paleo climate records emphasize interannual to multidecadal modes of variability"

23: The discount rate is given as a decision factor but this is not modeled in the paper. I suggest relegating mention of a discount rate to the introduction or discussion.

> We have removed the distracting mention of a discount rate

24: Suggest because instead of where.

> Our point here is that if variability can be identified and predicted -- which is not a given -- shorter design lives are preferred. The sentence now reads "Shorter design lives are preferred for situations where inter-annual to decadal variability can be successfully identified and predicted..."

38-39: Is this formatting of reference correct?

> Per the document "Brief Guide to AGU Style and Grammar" document available at https://publications.agu.org/brief-guide-agu-style-grammar/, "AGU’s latex template and APA style in reference management software do not include this exception. You do not need to update your manuscript with this exception; it will be applied by the production vendor during the copy-editing process."

41: perhaps a good place to insert a definition and example of operational and financial instruments? An example is given for a structural instrument and that is what people are most likely to understand already.

> This is a helpful suggestion. The sentence now reads "Rather, actors such as New York city have turned to a combination of structural (e.g., index insurance), operational (e.g., improved evacuation routes), and financial (eg, index insurance) investments for reducing vulnerability and increasing resilience to climate extremes." We note that all of these examples are contained in the City of New York report referenced. We believe that these examples are sufficient since a strict definition of different classes of instruments would substantially disrupt the structure of the paragraph.

50-51: Phrasing could be reworked; at minimum change this to these at the end of the sentence.

> The sentence now reads "In this paper we focus on the more narrow question of how the temporal structure of climate risk, and the uncertainties associated with its estimation, influence the answers to these questions."

53: comma after implications

> Added

67: perhaps a good place to define length of long-term short. Is this the interannual to multidecadal described in the abstract or the one-year term of a financial contract (line 59)?

> This is an important question, as we are certainly a bit vague here. The points are clearest in the limits of prediction at time scales less than one year or greater than a century; most real-world centuries are in between. To add some clarity, we have added another sentence with an example. This sentence reads "For example, the action that New York City can take today which best protects against uncertain hurricane risks over the 21st century could potentially be to purchase insurance and defer more permanent allocation of capital until some uncertainties are resolved." We hope that our wording does not imply that we have performed any analysis for New York City.

90-91: Phrasing is a bit obtuse.

> This sentence now reads "Secular change is not the only mechanism which can cause historical records to provide a biased view of future risk."

122: portend (singular)

> Fixed

Figure 1: Inconsistent capitalization. Can you add units?

> Working on this, but going to follow up RE units of American River

147: Recommend preserving the order you present the climate scenarios throughout the paper.

> This is reasonable. We order them (i) secular change only; (ii) LFV only; (iii) LFV plus secular change. This also mirrors the results.

185: Is the word ‘consider’ necessary in these paragraphs?

> We have changed two sentences. The first now reads "In the first case we fit a stationary model to the observed flood record, following...". The second now reads "Finally, we explicitly model LFV using a hidden Markov model (HMM)."

198: be consistent with use of acronyms (i.e. just say LFV).

> Sentence changed; see previous comment

205: suggest “log-normal distribution that is conditional only on the unobserved state
variables” (or S(t) instead of state).

> Thank you for the helpful suggestion

215 and 217: Can you say ‘that’ instead of ‘designed based on’? If these words are meaningful, can you elaborate?

> We agree that the wording was vague. The sentence now reads "An instrument whose design was based on projections with overestimated variance or positive bias will be..."

219: suggest “M, N, and

> This is helpful

### 2019-03-27 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
addressed all minor reviewer comments -- major comments still open

% Other package calls
\usepackage{
  amssymb, amsmath, % for math symbols
  booktabs, % for nice tables
  graphicx, % for figures
  physics, % for physics notation
  siunitx, % for SI notation
  apacite, % AGU style citations apparently
}

@@

% Key Points
\begin{keypoints}
  \item Climate risk varies in time over a project's finite planning period
  \item Importance of predicting different climate signals depends on extrapolation desired (planning period)
  \item Ability to identify and predict different climate signals depends on information available (\eg, data)
\end{keypoints}

% Abstract
\begin{abstract}
  The assessment and implementation of structural or financial instruments for climate risk mitigation requires projections of future climate risk over the operational life of each proposed instrument.
  A point often neglected in the climate adaptation literature is that the physical sources of predictability differ between projects with long and short planning periods: while historical and paleo climate records highlight the role of \acrlong{lfv} in modulating climate extremes at interannual to multidecadal time scales, \acrlong{acc} is expected to alter their occurrence at longer time scales.
  In this paper we present a set of stylized experiments to assess the uncertainties and biases involved in estimating future climate risk over a finite future period, given a limited observational record.
  These experiments consider both quasi-periodic and secular change for the underlying risk, as well as statistical models for estimating this risk from an $N$-year historical record.
  The uncertainty of \acrshort{ipcc}-like future scenarios is considered through an equivalent sample size $N$. 
  The relative importance of estimating the short- or long-term risk extremes depends on the investment life $M$ and the future discount rate for investment.
  Shorter design lives are preferred where inter-annual to decadal variability can be successfully identified and predicted, suggesting the importance of sequential investment strategies for adaptation. 
\end{abstract}

@@

Recent climate extremes such as floods, droughts, hurricanes, tornadoes, hailstorms, and heat waves have caused death and destruction, motivating investments in climate adaptation for the public and private sectors.
Further, rapid and continuing changes to global climate hazard and exposure underscore the need for adaptation strategies.
For example, population growth and urbanization have driven rapid increases in global exposure to events such as floods \citep{Jongman:2012cr} and tropical cyclones \citep{Peduzzi:2012iq}.
At the same time, anthropogenic modification of global and local climate processes affects the frequency, intensity, and location of extreme events \citep{IPCC:2012wt, Milly:2008dg, Shaw:2016bo}.
Even if mitigation efforts are successful, novel adaptation strategies are needed.

This need has motivated a multitude of approaches for estimating the probability distribution of future climate risk, and for choosing between different risk mitigation instruments based on these estimates \citep[see, \eg,][]{Merz:2014gf}.
Although climate risk has been traditionally managed with centrally planned structural instruments (\eg, a levee), the high price \citep{Papakonstantinou:2016ve}, environmental costs \citep{dugan:2010}, and vulnerability to biased climate projections \citep{lempert:2007} have recently slowed their implementation.
Instead, actors such as New York City have turned to a combination of structural, operational, and financial instruments for reducing vulnerability and increasing resilience to climate extremes \citep{CityofNewYork:2013uh}.
These instruments are not typically implemented in isolation or statically.
Instead, investment decisions made at each point in time affect the viability, costs, and benefits of future decisions, causing the system to trace a ``pathway'' through time \citep{Walker:2013gi,Haasnoot:2013im,Haasnoot:2015dh}.

Despite recent insights, important questions remain.
How should a portfolio of risk mitigation instruments be optimized?
How should one choose between permanent and transient instruments?
Under what conditions is a permanent, large infrastructure investment required, and what information is needed to recognize this threshold?
In this paper we focus on how the temporal structure of climate risk, and the uncertainties associated with estimating it, influence the answers to this questions.
We continue this section with three specific observations about climate risk which, while apparently obvious, have important and subtle implications which we examine in \cref{sec:methods,sec:results,sec:discussion-conclusions}.

@@

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own operational period, which may or may not match the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, \ie if long-term plans are a priority, this goal may be best accomplished through a series of flexible and adaptive instruments with short individual planning periods.
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

@@

Climate risk is governed by a variety of physical processes which occur on scales ranging from local and transient to global and permanent.
Of these processes, \gls{acc} has received the most attention in the climate adaptation literature and its influence on river floods, droughts, hurricanes, urban flooding, and many other climate hazards are well documented \citep[\eg,][]{Coumou:2012bc,Milly:2008dg,OGorman:2009hj,Trenberth:2003bj}.
Human activities can also affect climate risk through modification of local land or river systems \citep[see][]{Merz:2014gf}, and through changes in exposure to extremes \citep{baldassarre:2018,Jongman:2012cr}.
In combination, these effects highlight that the past may not be an adequate representation of future climate risk \citep[termed ``nonstationarity'' by][]{Milly:2008dg}.

Permanent or secular change is not, however, a prerequisite for the inadequacy of relying on historical records.
For example, \citet{Jain:2001hz} demonstrated that in a system with substantial \acrfull{lfv}, due, \eg, to \gls{enso}, the past $N$ years can be a poor proxy for the following $N$ years even when no secular change is present.
We illustrate this type of \gls{lfv} in \cref{fig:observed-lfv}, which shows a \SI{500}{year} drought reconstruction from the \gls{lbda} \citep{Cook:2010bz}, a \SI{100}{year} record of daily river stage on the American River at Folsom, and the wavelet average spectrum for both \citep{Torrence:1998jp,Roesch:wlBQQoIs}.
Peaks for the American River time series are apparent at approximately 2 and 15 years and in the \gls{lbda} time series at approximately 8, 20, and 64 years.
This is illustrated by the blue line in the top left panel of \cref{fig:observed-lfv}, which shows a \SI{20}{year} moving average of the \gls{lbda} time series.
A detailed analysis of these time series is beyond the scope of this paper, but we note that the high amplitude and long time periods of the quasi-periodic oscillations they exhibit are consistent with analyses of \gls{lfv} in other hydroclimate systems \citep{Kiem:2002kq,Swierczynski:2012km,Woollings:2014kd,Hodgkins:2017hw}.

@@

@@

Evaluating a particular risk mitigation instrument involves projecting climate risk over the $M$-year planning period.
Consequently, the physical mechanisms which impart predictability on the system differ between projects with long and short planning periods.
As illustrated in \cref{fig:conceptual-sketch} (a), the lifetime risk of a permanent structure with a \SI{100}{year} planning period depends on the magnitude and extent of future human activities, with very large associated uncertainty.
Even with a perfect climate model, these uncertainties will be large.
By contrast, this perfect climate model may usefully inform estimates of climate hazard over a three-year insurance contract with much less associated uncertainty.

Of course, scientists are not equipped with perfect models.
Since different physical processes control climate risk at different timescales, successful integration of climate projections into decision frameworks depends on identifying, and subsequently predicting, these processes.
A key question is whether the limited information in an $N$-year observational record permits the identification and projection of cyclical climate variability and secular change, and what the resulting bias and uncertainty portends for risk mitigation instruments with a planning period ranging from a few years to several decades.
As shown in \cref{fig:conceptual-sketch} (b), the combination of \gls{lfv}, stochastic variability, and secular change in a limited record can lead to large uncertainty in estimated future risk.
Although \cref{fig:conceptual-sketch} focuses on physical processes, similar conclusions would also be valid for the socioeconomic processes which drive exposure to floods and other hydroclimate hazards.

@@

We consider three scenarios for climate risk, which we define by the structure of the underlying climate signal:
\begin{enumerate*}[label= (\roman*)]
  \item \gls{lfv} only;
  \item \gls{lfv} plus secular change; and
  \item secular change only.
\end{enumerate*}
For each scenario, and for its identification from the $N$ year length historical data, the bias and variance of the estimated flood risk over the $M$ year design life relative to the ``true model'' are computed.
We repeat the simulations $J = 1000$ times for each combination of experiment parameters to obtain estimates of the expected bias and variance for each scenario given $M$ and $N$ (\cref{sec:methods-evaluating}).

@@

We first consider fitting a stationary model to the observed flood record, following classical assumptions of \gls{iid} sequences.
In this model annual-maximum streamflow are taken to follow a log-normal distribution with constant mean and variance.
The parameters of the model are fit  in a Bayesian framework to fully represent the posterior uncertainty, using the stan probabilistic computing package \citep{Carpenter:2017ke} with weakly informative priors \citep{gelman:2017,simpson:2017}.
The full model, including priors, is given in \cref{eq:log-normal-stationary}.

@@

We finally consider a model which explicitly represents \acrlong{lfv}.
A \gls{hmm} is a latent variable model in which the system being modeled is assumed to follow a Markov process with unobserved (\ie hidden) states $S(t)$ \citep{Rabiner:1986jk}.
The (unobserved) states evolve following a first-order Markov process, and the observed variable (\eg streamflow) depends only on the underlying state.
\Glspl{hmm} have been widely used for modeling streamflow sequences \citep{Bracken:2016ba} and \gls{enso} \citep{rojohernandez:2017}.
We fit  streamflow sequences using a \gls{hmm} with two states.
The model is fit using the Baum-Welch algorithm, assuming that the data follow a log-normal distribution conditional only on the state.
This algorithm simultaneously estimates the transition matrix of the Markov process and the conditional parameters of each distribution.
For simplicity, we fit only a two-state \gls{hmm} to each sequence.
Future floods are then estimated by simulating future states from the estimated transition matrix and then drawing $Q(t)$ conditional on the simulated state.

@@

Both estimation bias and estimation uncertainty affect the utility of a climate risk projection, as illustrated in \cref{fig:conceptual-bias-variance}.
An instrument designed based on overestimated variance and positive bias will be over-designed, either causing the risk manager to avoid the investment, given its higher cost, or will lead to unnecessary diversion of funds from other instruments.
Similarly, an instrument designed based on underestimated variance or negative bias may be under-designed, and thus fail to protect the user.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Bias-Variance-Sketch.pdf}
  \caption{
    Consequences of model bias or incorrect model representation of uncertainty.
    If an estimate has a positive bias and overestimates uncertainty, the instrument may be too expensive for the user.
    If an estimate has negative bias and underestimates uncertainty, it will be likely to fail.
  }\label{fig:conceptual-bias-variance}
\end{figure}

We evaluate both the estimation bias and estimation uncertainty.
For a given choice of $M$, $N$, generating model, we compare the synthetic streamflow sequence's $N$-year ``historical record'', and the $K=1000$ posterior simulations of future flows.
The quantity $\hat{p}_T$, the estimated expected number of floods per year, is taken by calculating, for each of the $K$ posterior simulations, the number of exceedances of the flood design threshold, then dividing by $M$ to get exceedances per year.
We then compute the variance of these $K$ estimates.
We further calculate the bias of $\hat{p}_T$ by averaging it across the $K$ samples and comparing this to the number of times the $M$-year ``future period'' of the synthetic streamflow sequence exceeds the flood design threshold.
Since the ``observed'' number of flood exceedances from the generating model is inherently noisy for an $M$-year period, we average the bias and variance across $J=1000$ different streamflow sequences to compute expected values of both.
These sequences are generated with the same underlying parameters, but the specific synthetic NINO3 sequence (or set of Markov states) may differ between the $J$ sequences.

@@

In this paper we considered how the temporal structure of the climate affects the potential for successful prediction over a finite $M$-year future period.
We began with three premises, or observations, about the nature of climate risk:
\begin{enumerate*}[label= (\roman*)]
  \item that planning decisions are made with finite horizons;
  \item that climate risk varies on many scales; and
  \item that the processes which dominate this risk over the planning period depend on the planning period itself.
\end{enumerate*}
Although the simulations presented here are neatly divided into secular change, \gls{lfv} only, and \gls{lfv} plus secular change, real-world hydroclimate time series exhibit \gls{lfv} on many timescales and several sources of (not necessarily linear) secular change, adding further informational and intrinsic uncertainties.

>>>>

% Other package calls
\usepackage{
  amssymb, amsmath,   % for math symbols
  apacite,            % AGU style citations apparently
  booktabs,           % for nice tables
  graphicx,           % for figures
  physics,            % for physics notation
  siunitx,            % for SI notation
  trackchanges,       % to track any new text
}

@@

% Key Points
\begin{keypoints}
  \item Climate risk varies over the planned lifespan of a project
  \item Importance of predicting different climate signals depends on extrapolation desired (planning period)
  \item Ability to identify and predict different climate signals depends on information available (\eg, data)
\end{keypoints}

% Abstract
\begin{abstract}
  The assessment and implementation of structural or financial instruments for climate risk mitigation requires projections of future climate risk over the operational life of each proposed instrument.
  A point often neglected in the climate adaptation literature is that the physical sources of predictability differ between projects with long and short planning periods: while historical and paleo climate records \add{emphasize} \remove{highlight the role of low-frequency variability (LFV) in modulating climate extremes at} interannual to multidecadal \remove{time scales} \add{modes of variability}, \acrlong{acc} is expected to alter their occurrence at longer time scales.
  In this paper we present a set of stylized experiments to assess the uncertainties and biases involved in estimating future climate risk over a finite future period, given a limited observational record.
  These experiments consider both quasi-periodic and secular change for the underlying risk, as well as statistical models for estimating this risk from an $N$-year historical record.
  The uncertainty of \acrshort{ipcc}-like future scenarios is considered through an equivalent sample size $N$. 
  The relative importance of estimating the short- or long-term risk extremes depends on the investment life $M$\remove{ and the future discount rate for investment}.
  Shorter design lives are preferred \add{for situations} where inter-annual to decadal variability can be successfully identified and predicted, suggesting the importance of sequential investment strategies for adaptation. 
\end{abstract}

@@

Recent climate extremes such as floods, droughts, hurricanes, tornadoes, hailstorms, and heat waves have caused death and destruction, motivating investments in climate adaptation for the public and private sectors.
Further, rapid and continuing changes to global climate hazard and exposure underscore the need for adaptation strategies.
For example, population growth and urbanization have driven rapid increases in global exposure to events such as floods \citep{Jongman:2012cr} and tropical cyclones \citep{Peduzzi:2012iq}.
At the same time, anthropogenic modification of global and local climate processes affects the frequency, intensity, and location of extreme events \citep{IPCC:2012wt, Milly:2008dg, Shaw:2016bo}.
Even if \add{future} mitigation efforts are successful, \add{existing levels of atmospheric $\text{CO}_2$ and ocean heat content mean that} novel adaptation strategies are needed.

This need has motivated a multitude of approaches for estimating the probability distribution of future climate risk, and for choosing between different risk mitigation instruments based on these estimates \citep[see, \eg,][]{Merz:2014gf}.
Although climate risk has been traditionally managed with centrally planned structural instruments (\eg, a levee), the high price \citep{Papakonstantinou:2016ve}, environmental costs \citep{dugan:2010}, and vulnerability to biased climate projections \citep{lempert:2007} have recently slowed their implementation.
\remove{Instead}\add{Rather}, actors such as New York City have turned to a combination of structural\add{ (\eg, a stormwater barrier)}, operational\add{ (\eg, improved evacuation routes)}, and financial\add{ (\eg, index insurance)} instruments for reducing vulnerability and increasing resilience to climate extremes \citep{CityofNewYork:2013uh}.
These instruments are not typically implemented in isolation or statically.
Instead, investment decisions made at each point in time affect the viability, costs, and benefits of future decisions, causing the system to trace a ``pathway'' through time \citep{Walker:2013gi,Haasnoot:2013im,Haasnoot:2015dh}.

Despite recent insights, important questions remain.
How should a portfolio of risk mitigation instruments be optimized?
How should one choose between permanent and transient instruments?
Under what conditions is a permanent, large infrastructure investment required, and what information is needed to recognize this threshold?
In this paper we focus on \add{the more narrow question of} how the temporal structure of climate risk, and the uncertainties associated with \add{its estimation}\remove{estimating it}, influence the answers to these questions.
We continue this section with three specific observations about climate risk which, while apparently obvious, have important and subtle implications\add{,} which we examine in \cref{sec:methods,sec:results,sec:discussion-conclusions}.

@@

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own operational period, which may or may not match the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, \ie if long-term plans are a priority, this goal may be best accomplished through a series of flexible and adaptive instruments with short individual planning periods.
\add{For example, the action that New York City can take today which best protects against uncertain hurricane risks over the 21st century could potentially be to purchase insurance and defer more permanent allocation of capital until some uncertainties are resolved.}
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

@@

Climate risk is governed by a variety of physical processes which occur on scales ranging from local and transient to global and permanent.
Of these processes, \gls{acc} has received the most attention in the climate adaptation literature and its influence on \add{some} river floods, droughts, hurricanes, urban flooding, and many other climate hazards \remove{are}\add{has been the subject of substantial investigation} \remove{well documented} \citep[\eg,][]{Coumou:2012bc,Milly:2008dg,OGorman:2009hj,Trenberth:2003bj}.
Human activities can also affect climate risk through modification of local land or river systems \citep[see][]{Merz:2014gf}, and through changes in exposure to extremes \citep{baldassarre:2018,Jongman:2012cr}.
In combination, these effects highlight that the past may not be an adequate representation of future climate risk \citep[termed ``nonstationarity'' by][]{Milly:2008dg}.

\remove{Permanent or secular change is not, however, a prerequisite for the inadequacy of relying on historical records.}
\add{Secular change is not the only mechanism which can cause historical records to provide a biased view of future risk.}
For example, \citet{Jain:2001hz} demonstrated that in a system with substantial \acrfull{lfv}, due, \eg, to \gls{enso}, the past $N$ years can be a poor proxy for the following $N$ years even when no secular change is present.
We illustrate this type of \gls{lfv} in \cref{fig:observed-lfv}, which shows a \SI{500}{year} drought reconstruction from the \gls{lbda} \citep{Cook:2010bz}, a \SI{100}{year} record of daily river stage on the American River at Folsom, and the wavelet average spectrum for both \citep{Torrence:1998jp,Roesch:wlBQQoIs}.
Peaks for the American River time series are apparent at approximately 2 and 15 years and in the \gls{lbda} time series at approximately 8, 20, and 64 years.
This is illustrated by the blue line in the top left panel of \cref{fig:observed-lfv}, which shows a \SI{20}{year} moving average of the \gls{lbda} time series.
A detailed analysis of these time series is beyond the scope of this paper, but we note that the high amplitude and long time periods of the quasi-periodic oscillations they exhibit are consistent with analyses of \gls{lfv} in other hydroclimate systems \citep{Kiem:2002kq,Swierczynski:2012km,Woollings:2014kd,Hodgkins:2017hw}.

@@

\add{A WHOLE PARAGRAPH ABOUT HURST EFFECT}

@@

Evaluating a particular risk mitigation instrument involves projecting climate risk over the $M$-year planning period.
Consequently, the physical mechanisms which impart predictability on the system differ between projects with long and short planning periods.
As illustrated in \cref{fig:conceptual-sketch} (a), the lifetime risk of a permanent structure with a \SI{100}{year} planning period depends on the magnitude and extent of future human activities, with very large associated uncertainty.
Even \remove{with} \add{in the idealized, and unrealistic, case of} a perfect climate model, these uncertainties will be large.
By contrast, this perfect climate model may usefully inform estimates of climate hazard over a three-year insurance contract with much less associated uncertainty.

Of course, scientists are not equipped with perfect models.
Since different physical processes control climate risk at different timescales, successful integration of climate projections into decision frameworks depends on identifying, and subsequently predicting, these processes.
A key question is whether the limited information in an $N$-year observational record permits the identification and projection of cyclical climate variability and secular change, and what the resulting bias and uncertainty portend\remove{s} for risk mitigation instruments with a planning period ranging from a few years to several decades.
As shown in \cref{fig:conceptual-sketch} (b), the combination of \gls{lfv}, stochastic variability, and secular change in a limited record can lead to large uncertainty in estimated future risk.
Although \cref{fig:conceptual-sketch} focuses on physical processes, similar conclusions would also be valid for the socioeconomic processes which drive exposure to floods and other hydroclimate hazards.

@@

We consider three scenarios for climate risk, which we define by the structure of the underlying climate \annote{signal}{changed the order}:
\begin{enumerate*}[label= (\roman*)]
  \item secular change only;
  \item \gls{lfv} only; and
  \item \gls{lfv} plus secular change.
\end{enumerate*}
For each scenario, and for its identification from the $N$ year length historical data, the bias and variance of the estimated flood risk over the $M$ year design life relative to the ``true model'' are computed.
We repeat the simulations $J = 1000$ times for each combination of experiment parameters to obtain estimates of the expected bias and variance for each scenario given $M$ and $N$ (\cref{sec:methods-evaluating}).

@@

\add{In the first case we} \remove{We first consider fitting}\add{fit} a stationary model to the observed flood record, following classical assumptions of \gls{iid} sequences.
In this model annual-maximum streamflow are taken to follow a log-normal distribution with constant mean and variance.
The parameters of the model are fit  in a Bayesian framework to fully represent the posterior uncertainty, using the stan probabilistic computing package \citep{Carpenter:2017ke} with weakly informative priors \citep{gelman:2017,simpson:2017}.
The full model, including priors, is given in \cref{eq:log-normal-stationary}.

@@

\remove{We finally consider}\add{Finally, we explicitly model} \remove{a HMM which explicitly represents}\gls{lfv} \add{using a} \gls{hmm}.
A \gls{hmm} is a latent variable model in which the system being modeled is assumed to follow a Markov process with unobserved (\ie hidden) states $S(t)$ \citep{Rabiner:1986jk}.
The (unobserved) states evolve following a first-order Markov process, and the observed variable (\eg streamflow) depends only on the underlying state.
\Glspl{hmm} have been widely used for modeling streamflow sequences \citep{Bracken:2016ba} and \gls{enso} \citep{rojohernandez:2017}.
We fit  streamflow sequences using a \gls{hmm} with two states.
The model is fit using the Baum-Welch algorithm, assuming that the data follow a log-normal distribution \remove{conditional only on the state}\add{that is conditional only on the unobserved state variables}.
This algorithm simultaneously estimates the transition matrix of the Markov process and the conditional parameters of each distribution.
For simplicity, we fit only a two-state \gls{hmm} to each sequence.
Future floods are then estimated by simulating future states from the estimated transition matrix and then drawing $Q(t)$ conditional on the simulated state.

@@

Both estimation bias and estimation uncertainty affect the utility of a climate risk projection, as illustrated in \cref{fig:conceptual-bias-variance}.
An instrument \add{whose design was based on projections with} \remove{designed based on} overestimated variance \remove{and}\add{or} positive bias will be over-designed, either causing the risk manager to avoid the investment, given its higher cost, or will lead to unnecessary diversion of funds from other instruments.
Similarly, an instrument designed based on underestimated variance or negative bias may be under-designed, and thus fail to protect the user.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Bias-Variance-Sketch.pdf}
  \caption{
    Consequences of model bias or incorrect model representation of uncertainty.
    If an estimate has a positive bias and overestimates uncertainty, the instrument may be too expensive for the user.
    If an estimate has negative bias and underestimates uncertainty, it will be likely to fail.
  }\label{fig:conceptual-bias-variance}
\end{figure}

We evaluate both the estimation bias and estimation uncertainty.
For a given choice of $M$, \add{and} $N$, generating model, we compare the synthetic streamflow sequence's $N$-year ``historical record'', and the $K=1000$ posterior simulations of future flows.
The quantity $\hat{p}_T$, the estimated expected number of floods per year, is taken by calculating, for each of the $K$ posterior simulations, the number of exceedances of the flood design threshold, then dividing by $M$ to get exceedances per year.
We then compute the variance of these $K$ estimates.
We further calculate the bias of $\hat{p}_T$ by averaging it across the $K$ samples and comparing this to the number of times the $M$-year ``future period'' of the synthetic streamflow sequence exceeds the flood design threshold.
Since the ``observed'' number of flood exceedances from the generating model is inherently noisy for an $M$-year period, we average the bias and variance across $J=1000$ different streamflow sequences to compute expected values of both.
These sequences are generated with the same underlying parameters, but the specific synthetic NINO3 sequence (or set of Markov states) may differ between the $J$ sequences.

@@

In this paper we considered how the temporal structure of the climate affects the potential for successful prediction over a finite $M$-year future period.
We began with three premises, or observations, about the nature of climate risk:
\begin{enumerate*}[label= (\roman*)]
  \item that \remove{planning decisions are made with finite horizons}\add{different climate risk mitigation instruments have different planned lifespans};
  \item that climate risk varies on many scales; and
  \item that the processes which dominate this risk over the planning period depend on the planning period itself.
\end{enumerate*}
Although the simulations presented here are neatly divided into secular change, \gls{lfv} only, and \gls{lfv} plus secular change, real-world hydroclimate time series exhibit \gls{lfv} on many timescales and several sources of (not necessarily linear) secular change, adding further informational and intrinsic uncertainties.
